### 2020-03-03 ChapterBackground/chapterBackground.tex
Fixed: Typos in Background

Client-authoritative physics creates consistency problems within the simulation, as the physics states on different clients will quickly diverge (discussed further in \ref{divergingResults}). This is especially true with high latencies and limited bandwith experienced between clients. Client-side resources, both computational and network must be sacrificied in order to attempt to reach consensus on the physics state, however, inconsistencies will always be present.  Gameplay aspects of games, such as life/death and score decisions require a high-level of consistency in order to maintain fairness \cite{savery2014consistency}. Due to these consistency problems, physics is unable to influence gameplay without sacrifices to fairness being made.

>>>>

Client-authoritative physics creates consistency problems within the simulation, as the physics states on different clients will quickly diverge (discussed further in \ref{divergingResults}). This is especially true with high latencies and limited bandwidth experienced between clients. Client-side resources, both computational and network must be sacrificed in order to attempt to reach consensus on the physics state, however, inconsistencies will always be present.  Gameplay aspects of games, such as life/death and score decisions require a high-level of consistency in order to maintain fairness \cite{savery2014consistency}. Due to these consistency problems, physics is unable to influence gameplay without sacrifices to fairness being made.
